|

### 2021-09-09 appendix/appendix.Rmd
appendix table fix

aux3 <- descrTable(~.-usemeta2,
                   aux, y = aux$usemeta2,
                   show.p.overall = F,
                   show.all = T)
export2md2(aux3,
           caption = "Descriptive Statistics of Moderators",
           format  = "latex")
```

>>>>

aux3 <- descrTable(~.-usemeta2,
                   aux, y = aux$usemeta2,
                   show.p.overall = F,
                   show.all = T)
export2md2(aux3,
           caption = "Descriptive Statistics of Moderators",
           format  = "latex")

```
